Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2001-01-01 paper.tex
Fix typo
Add description of HMNS configuration

\subsection{Hypermassive Neutron Star Remnant:
  Testing Everything}
\label{ssec:test_disk_comparison}
Total and relative number and energy luminosities for the disk evolved
in \cite{fouc2016-m1_evolve_n}.
Agreement better than 10\%.
\todo{get accurage M1 numbers from Francois}

\begin{figure}
  \includegraphics[width=\columnwidth]{production-colormap-merid-rho}
  \caption{A meridional slice of density in the hypermassive neutron
    star and disk configuration.}
  \label{fig:nsns_rho_merid}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{production-colormap-equat-temp}
  \caption{A meridional slice of temperature in the hypermassive neutron
    star and disk configuration.}
  \label{fig:nsns_temp_equat}
\end{figure}

>>>>

\subsection{Hypermassive Neutron Star Remnant:
  Testing Everything}
\label{ssec:test_disk_comparison}
The merger of two neutron stars by gravitational wave emission produces a
postmerger configuration composed of a single neutron star surrounded by a disk.
Because of the strong differential rotation of the remnant it temporarily avoids
collapse to a black hole, even if its mass exceeds the threshold of dynamical
instability for a rigidly rotating neutron star \cite{duez2009-review}.
These objects are called hypermassive neutron stars.

Such a configuration was modeled by \cite{fouc2016-m1_nsns} by
evolving the final inspiral and merger of two identical neutron stars of
isolated gravitational mass 1.2~$M_{\odot}$. The postmerger configuration
was evolved using an M1 transport scheme for the neutrinos, evolving the
energy density, number density, and energy flux \cite{fouc2016-m1_evolve_n}
for $\sim10\,{\rm ms}$ following merger, defined as the time of the peak of the
gravitational wave strain.

We used a single time snapshot of the volume data from that configuration
at $t=11\,{\rm ms}$ after merger (see
Figs.~\ref{fig:nsns_rho_merid}--\ref{fig:nsns_temp_equat})
sampling the neutrino fields with ray tracing to compare to some
measures of the field computed from the M1 transport simulation.

\begin{figure}
  \includegraphics[width=\columnwidth]{production-colormap-merid-rho}
  \caption{A meridional slice of density in the hypermassive neutron
    star and disk configuration.
    The distorted rectangular boundaries are the boundaries of the grid
    used in the numerical simulation, which employs a coordinate mapping to
    concentrate points near the central object.}
  \label{fig:nsns_rho_merid}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{production-colormap-equat-temp}
  \caption{An equatorial slice of temperature in the hypermassive neutron
    star and disk configuration.}
  \label{fig:nsns_temp_equat}
\end{figure}

In Tab.~\ref{tab:nsns_rt_vs_m1} we present total and relative number and
energy luminosities for this configuration.
With scattering turned off, ray tracing errors are as large as 250\%
(for heavy lepton energy luminosities).
But with scattering turned on, agreement is better than 20\%, and
in most cases much better.
\todo{get accurage M1 numbers from Francois}
